Capstone Movielens Report

### 2025-12-13 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the previous commit.

In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.loess_de.args.de_bias.dat) argument) is created and returned by the following functions described above in *this Section*:

@@

In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in *this Section*:

@@

::: {.noteblock data-latex=""}
This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) auxiliary function described above in *this Section* to compute the *MSE* for the *UMGYDE Model* and then calculates the *square root* of the obtained result.
:::

In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in *this Section*:

@@

Validates the *UMGYD Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in section [UMGYDE Model: Regularization] of *this Appendix*.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.

The function calculates *Root Squared Error (RMSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

::: {.noteblock data-latex=""}
This function internally calls the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.

The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is shown below:
```{r eval=FALSE}
```

>>>>

In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.loess_de.args.de_bias.dat) argument) is created and returned by the following functions described above in this section:

@@

In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in this section:

@@

::: {.noteblock data-latex=""}
This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) auxiliary function described above in this section to compute the *MSE* for the *UMGYDE Model* and then calculates the *square root* of the obtained result.
:::

In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in this section:

@@
